Data leakage - does imputation before or after splitting matter?

### 2022-11-02 workflow/notebooks/data-leakage-imputation.Rmd

TODO histogram showing # of NA's in OTU columns instead of barplot (too many OTUs for barplot)
```{r plot_histogram}
plot_histogram = function(dat) {
  missing.values <- dat %>%
    pivot_longer(everything(), names_to = "key", values_to = "val") %>%
    mutate(is.missing = is.na(val)) %>% 
    filter(is.missing)
  missing.values %>%
    ggplot() +
      geom_histogram(aes(key), stat="count", color="black", bins=2) +
      labs(x='variable', y="number of missing values", title='Number of missing values')
}
```
```{r check_works_with_simple_frame}
dat <- data.frame(x1 = c(NA, 5, 5, NA, 1, 2),
                   x2 = c(1, 2, 3, NA, 5, 6),
                   x3 = 1)
temp <- colSums(is.na(dat)) 
head(temp)
sum(temp)
missing.values <- dat %>%
    pivot_longer(everything(), names_to = "key", values_to = "val") %>%
    mutate(is.missing = is.na(val)) %>% 
    filter(is.missing)
missing.values %>%
  ggplot() +
    geom_histogram(aes(key), stat="count", color="black", bins=2) +
    labs(x='variable', y="number of missing values", title='Number of missing values')
```

>>>>

TODO histogram showing # of NA's in OTU columns instead of barplot (too many OTUs for barplot)

TODO functions to find NAs and create histogram

```{r plot_histogram}
plot_histogram = function(dat) {
  missing.values <- dat %>%
    pivot_longer(everything(), names_to = "key", values_to = "val") %>%
    mutate(is.missing = is.na(val)) %>% 
    filter(is.missing)
  missing.values %>%
    ggplot() +
      geom_histogram(aes(key), stat="count", color="black", bins=2) +
      labs(x='variable', y="number of missing values", title='Number of missing values')
}
```
```{r check_works_with_simple_frame}
dat <- data.frame(x1 = c(NA, 5, 5, NA, 1, 2),
                   x2 = c(1, 2, 3, NA, 5, 6),
                   x3 = 1)
temp <- colSums(is.na(dat)) 
head(temp)
sum(temp)
missing.values <- dat %>%
    pivot_longer(everything(), names_to = "key", values_to = "val") %>%
    mutate(is.missing = is.na(val)) %>% 
    filter(is.missing)
missing.values %>%
  ggplot() +
    geom_histogram(aes(key), stat="count", color="black", bins=2) +
    labs(x='variable', y="number of missing values", title='Number of missing values')
```
